О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Note about charactristic

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ (and every characteristic $q$~--- see~\cite{kurz2005characteristic} for details)
there exists a facher set $M\in\mathfrak{M}(2,n)$ (with the desired characteristic~\cite[Theorem 5]{our-vmmsh-2018}).
In~\cite{antonov2008maximal}, the facher sets of characteristic 1 are called \textit{semi-crabs} and investigated.

>>>>

\begin{definition}
	\cite{kurz2005characteristic}
	A \textit{characteristic} of an integral point set $M$ is such a squarefree number $q$,
	that for any points $M_1, M_2, M_3 \in M$ the area of triangle $M_1 M_2 M_3$
	is $p\sqrt{q}$, where $p$ is rational.
\end{definition}
For given integral point set, the characteristic is determined uniquely.

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ and every characteristic $q$
there exists a facher set $M\in\mathfrak{M}(2,n)$ with characteristic $q$~\cite[Theorem 5]{our-vmmsh-2018}.
In~\cite{antonov2008maximal}, the facher sets of characteristic 1 are called \textit{semi-crabs} and investigated.
